---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Open Scoring API Client for R

<!-- badges: start -->
[![R-CMD-check](https://github.com/jakub-jedrusiak/openscoring/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jakub-jedrusiak/openscoring/actions/workflows/R-CMD-check.yaml)
![CRAN/METACRAN Version](https://img.shields.io/cran/v/openscoring)
[![codecov](https://codecov.io/gh/jakub-jedrusiak/openscoring/graph/badge.svg?token=nH9qzHWEqR)](https://codecov.io/gh/jakub-jedrusiak/openscoring)
<!-- badges: end -->

Creativity research involves the need to score open-ended problems. Usually done by humans, automatic scoring using AI becomes more and more accurate. This package provides a simple interface to the 'Open Scoring' API, leading creativity scoring technology by Organiscak et al. ([2023](https://doi.org/10.1016/j.tsc.2023.101356)). With it, you can score your own data directly from an R script.

## Installation

Install the released version of openscoring from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("openscoring")
```

You can install the development version of openscoring from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jakub-jedrusiak/openscoring")
```

## Example

```{r example}
library(openscoring)

df <- tibble::tibble(
  stimulus = c("brick", "hammer", "sponge"),
  response = c("butter for trolls", "make Thor jealous", "make it play in a kids show")
)

df

scored_df <- oscai(df, stimulus, response, model = "davinci2")

scored_df
```
